Untitled

### 2020-09-01 Figures_main_text/Figure3_effect_sizes_grouped.Rmd
pfinal edits

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6}

library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)

load("effect_size_species/effect_size_total.RData")
png("Figure4.png", width = 11000, height = 5000, res = 1500)

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6}
#Load libraries
library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)

#Load data
#This data is generated in analysis in the "Effect sizes_total.R" file
#Please see Script-->Analysis
#Now figure 3 in main text
setwd("~/R_projects/Hp_pollen_experiment")
load("Data/RData/effect_size_total.RData")
#save image
#png("Figure4.png", width = 11000, height = 5000, res = 1500)
